Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-01-31 writeups/psycMethods/psycMethods.tex
foo

This study expands on previous work that has tested retrieval models on large-scale datasets.
It focuses specifically on how two state-of-the-art declarative memory retrieval models (ACT-R Bayesian and vector-based) can be improved by testing these models on two real-world tagging tasks.
One primary objective is to compare the random permutation vector-based model to ACT-R's Bayesian declarative memory theory when large datasets are used for each model. 
Another objective is to improve each model, and measure how incorporating the strengths of each model into the other (i.e., modifying model components) influences accuracy.
For example, it is currently unexplored how a vector-based model can be modified to retrieve results that are based not only on context, but also on the prior odds that a particular item in memory will be needed again.
Large-scale datasets were used throughout the model development and evaluation process.
This provides an ideal testing environment for constraints and assumptions for each theory to be rapidly tested and new model components to be hypothesized and quickly evaluated.

@@

ACT-R \parencite{Anderson2007} is a cognitive architecture that formalizes how each cognitive process of the mind (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of the architecture that models the timing, learning, and forgetting processes that make up declarative memory storage and retrieval.
The equations that make up this system were derived from a rational analysis of declarative memory retrieval \parencite{Anderson1989}.
That is, given the task of retrieving a chunk of information from declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likelihood of needing retrieval again, given the prior history of exposure to the chunk.
These chunk prior probabilities are then adjusted for the current context, so that the posterior probabilities represent the likelihood that a chunk is needed, given prior odds and adjusted by current environment state.

@@

For vector-based systems, each word is represented by an environment vector $e_{i}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix, which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from position-independent word co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

A custom tokenization algorithm created by \textcite{Owoputi2013} was used to chunk the words in the text.
This algorithm was specifically created for tokenizing Twitter content.
However, during testing it was also found to be robust and well-suited for StackOverflow content.
The initial model results with the new tokenizer were qualitatively similar to the model results found in \textcite{Stanley2013} where the Python Natural Language Processing (NLP) toolkit \parencite{Bird2009} was used.
So the same tokenization algorithm from \textcite{Owoputi2013} was used for both StackOverflow and Twitter, since it seemed beneficial to use the same algorithm for both datasets to make comparisons across datasets more equitable.

@@

\textcite{Owoputi2013}'s algorithm handles basic word stemming (e.g., removing ``ed'' and ``ing'' endings), but
with the StackOverflow dataset, it is also possible to convert synonym tags to canonical base tags, since the community maintains a tag-synonym database.
This can be thought of as semantic stemming, where two words with identical meaning are converted to the same canonical word.
So tags used for the post were converted to their root tag when possible.

@@

The base-level ($B_{i}$) component in Table \ref{tabACTRBLLModel} is different than the $B_{i}$ used in \textcite{Stanley2013} (Table \ref{tabModACTRModel}).
\citeauthor{Stanley2013} assumed no time dependence, no decay rate, and that the $B_{i}$ is simply a log-odds computation of the probability that each chunk is likely to be presented again, given past frequency.
If a decay rate of 0 is used on the optimized learning form of $B_{i}$, then the equation collapses to $log \left ( n_{i} \right )$,
which is a nonlinear transformation of the $B_{i}$ used by \citeauthor{Stanley2013} ($log \frac{p_{i}}{1-p_{i}}$).
Both forms maintain the same rank ordering, so they should produce similar results.

@@

Given this, it may be worthwhile to use the standard form instead of the optimized learning form when declarative memory is modeled across a broader range of tasks.
However, this should not be taken as a strong recommendation,
since the performance benefits seen in this study could simply be due to the fact that the declarative memory retrievals span across a large period of time, which is not the case for all tasks.
Nonetheless, the only real reason not to use the standard form is due to computational resource limitations.
Since this is becoming less of an issue as hardware speed increases, it may be time to reconsider the default form of base-level learning used in ACT-R.
It may be the case that the optimized learning form of the equation is no longer computationally necessary.
And if the standard form is used as the default (or simply tried in another experiment),
the results from this study suggest that the optimal decay rate value should be set slightly higher (\num{0.8}) than the default when optimized learning is used (\num{0.5}).

@@

The ``no processing'' plot shows the size of the spikes when high-frequency words are not removed.
The entropy plot shows how the size decreases by more than an order of magnitude after the entropy weighting measure is used.
The cutoff for the frequency plot was chosen such that the plot looks similar to the entropy plot, with spikes around the same size.
The cutoff that produced the frequency plots in Figures \ref{figContextCutoffSO} and \ref{figContextCutoffT} is where a word represents more than \num{.04}\% of total occurrences in the dataset.
This may or may not be equal to the value for \textcite{Sahlgren2008}, since that number was expressed in total observations (not as a percentage), and the total number of words in the dataset was not given.

@@

Plots for the three methods of handling stop words for the random permutation model on the StackOverflow dataset are shown in Figure \ref{figContextStopRPSO}.
In the plot, if the model name includes ``full'' then all model components are included.
When the model components are enumerated, then at least one of the components is left out.
So, for example, the ``standard prior model relaxed across posts'' means that only the prior model component was used when determining activation. 
As another example, ``RP only title with freq'' means that only the title context component of the random permutation model was used, and that stop words were handled using the frequency filtering technique.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsSOPerm-crop.pdf}}}
  \caption{
    Stop-word techniques for the random permutation model for StackOverflow.
    The five methods for handling stop words are shown both for the title model component in isolation and the full model.
    ``Stoplist'', ``freq'', ``entropy'' are the stoplist removal method, removal based on frequency count, and weighting based entropy metric.
}
  \label{figContextStopRPSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsTPerm-crop.pdf}}}
  \caption{
  Stop-word techniques for the random permutation model for Twitter.
  The five methods for handling stop words are shown both for the context model component (i.e., no prior term) and the full model.
}
  \label{figContextStopRPT}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsSOSji-crop.pdf}}}
  \caption{Stop-word techniques for the Bayesian model for StackOverflow}
  \label{figContextStopBSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsTSji-crop.pdf}}}
  \caption{Stop-word techniques for the Bayesian model for Twitter}
  \label{figContextStopBT}
\end{figure}

@@

The number of documents used to build the co-occurrence matrix has been shown to influence model accuracy \parencite{Sahlgren2008}, so this was the second architectural concern that was examined.
The default number of documents used to build the co-occurrence matrix was \num{1000000} for StackOverflow and \num{3000000} for Twitter.
In order to see how accuracy changed as function of corpus size, 
co-occurrence matrices for a range of smaller corpus sizes were built.

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsSO-crop.pdf}}}
  \caption{Random permutation model accuracy when using log-odds transformation on context for StackOverflow}
  \label{figContextLogoddsSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsT-crop.pdf}}}
  \caption{Random permutation model accuracy when using log-odds transformation on context for Twitter}
  \label{figContextLogoddsT}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-orderT-crop.pdf}}}
  \caption{Model accuracy for various word order methods for the random permutation model for Twitter}
  \label{figContextOrder}
\end{figure}

@@

The general discussion is separated into two parts.
The first section will describe the overall results, reemphasize key findings, and discuss the theoretical implications of each key finding.
The final section will describe future directions for the research.

@@

These results provide support for the idea that choosing a hashtag when composing a tweet and tagging a StackOverflow post is akin to a declarative memory retrieval process.
However, both models were not 100 percent accurate, and the amount of variance left to predict was is larger than what would be observed if retrieval noise is included in the model.
One possibility that seems likely is that the tag selection process includes other processes besides just declarative memory retrieval
(e.g., strategic processes, determining the number of tags to employ, attempts to add humor).

@@

Even with the large datasets used in this research, there was not enough data on each individual user to build up separate co-occurrence matrices for them.
That is, the context component of the declarative memory models used in this resaerch was formed as a collection of observed co-occurrences across all individuals.
Nonetheless, the prior component for the models was customized for each individual (except in the Twitter popular hashtags dataset when it was not possible).
Ideally, both components would be customized to the individual, and it remains an open question how much accuracy is influenced by using an aggregate or custom context component in the models.
One practical approach that might be considered for future research:
Use a large corpus to stand up an initial aggregate co-occurrence matrix (e.g., the Wikipedia corpus),
then overlay the specific co-occurrences observed for each user on top of this base to create a customized matrix for each user,
and then test model accuracy with and without the custom overlay.

@@

One alternative explanation is that the entropy weighting measure was needed because the contextual co-occurrence matrix for this research was not yet stable, even with these large dataset sizes.
If the matrix was not yet stable, then by chance certain stop words would contribute more net activation to specific tags and introduce noise into the retrieval process for that tag.
So further weighting the contribution of these stop words by leveraging the attentional weight term ensured that this noise was not introduced into the system.
If this is the case, it would be intersting to see how large a dataset is required to not need to modify the attentional weight term.
However even if this is the case, the random permutation model would not be fixed by larger dataset sizes,
since this model simply adds environment vectors to produce the current context vector and has no mechanism (unlike Bayesian normalization) for weighting the contribution of an environment vector.

@@

@@

\subsubsection{Which Model is Better?}

After including the prior and entropy components for both models, overall accuracy was similar for the Bayesian and random permutation models for this task.
So it is unclear with this research precisely which model is more cognitively plausible.
However, there were two areas in particular where model performance showed relatively large differences: accuracy change as a function of corpus size and reliance on entropy weighting.
These areas could be used in future research to more directly challenge the models.
For example, a domain could be picked where enough data is collected to build a custom co-occurrence matrix for each user.
Then one could look at model accuracy over time for each user as the co-occurrence matrix is increased to see if the trajectory is more accurately modeled by a random permutation (more accurate with lower N) or Bayesian (more accurate with higher N) model.
Further, if a large-scale domain is picked and it is shown that the Bayesian model does not require entropy weighting for the co-occurrence matrix after the representations are fully stabilized,
then this would provide a case where the two models are dramatically different: the random permutation model would require explicitly weighting the stop words (entropy weighting) while the Bayesian model would not.

>>>>

This study expands on previous work that has tested retrieval models on large-scale datasets.
It focuses specifically on how two state-of-the-art declarative memory retrieval models (ACT-R Bayesian and random permutation vector-based) can be improved by testing these models on two real-world tagging tasks.
One primary objective is to compare the random permutation vector-based model to ACT-R's Bayesian declarative memory theory when large datasets are used for each model. 
Another objective is to improve each model, and measure how incorporating the strengths of each model into the other (i.e., modifying model components) influences accuracy.
For example, it is currently unexplored how a vector-based model can be modified to retrieve results that are based not only on context, but also on the prior odds that a particular item in memory will be needed again.
Large-scale datasets were used throughout the model development and evaluation process.
This provides an ideal testing environment for constraints and assumptions for each theory to be rapidly tested and new model components to be hypothesized and quickly evaluated.

@@

ACT-R \parencite{Anderson2007} is a cognitive architecture that formalizes how each cognitive process of the mind (e.g., memory, learning, visual and motor) interacts to produce behavior.
The declarative memory system is a component of the architecture that models the timing, learning, and forgetting processes that make up declarative memory storage and retrieval.
At the core of the system is the concept of a ``chunk'': the representation of a piece of knowledge (e.g., a word).
The equations that make up this system were derived from a rational analysis of declarative memory retrieval \parencite{Anderson1989}.
That is, given the task of retrieving a chunk of information from declarative memory,
the current context (i.e., external and internal environment state), and past experience (i.e., prior memories and exposure), 
what is the optimal behavior (i.e., the optimal chunk to retrieve from memory)?
Using Bayesian reasoning, each chunk of information in declarative memory can be assigned a prior likelihood of needing retrieval again, given the prior history of exposure to the chunk.
These chunk prior probabilities are then adjusted for the current context, so that the posterior probabilities represent the likelihood that a chunk is needed, given prior odds and adjusted by current environment state.

@@

For vector-based systems, each word is represented by an environment vector $e_{i}$ that is nearly orthogonal to all other words' environment vectors.
The number of dimensions for these vectors is much less than the number of rows in a full word co-occurrence matrix (typically around 2,000 - 4,000), which is how vector-based systems represent information in a much more compact space.
Paired with each environment vector ($e_{i}$) is a memory vector ($m_{i}$) that contains the summed representation of all other environment vectors that have co-occurred with that $e_{i}$ environment vector.
These memory vectors can contain environment vectors from position-independent word co-occurrence information ($c_{i}$) and word order information ($o_{i}$), which can be combined into a single representation ($m_{i}$).
Over time, memory vectors accumulate a distributed representation of the most common environment vectors that co-occurred with them.

@@

A custom tokenization algorithm created by \textcite{Owoputi2013} was used to chunk the words in the text.
This algorithm was specifically created for tokenizing Twitter content.
However, during testing it was also found to be robust and well-suited for StackOverflow content.
The initial model results with the new tokenizer were qualitatively similar to the model results found in \textcite{Stanley2013} where the Python Natural Language Processing (NLP) toolkit \parencite{Bird2009} was used.
So the same tokenization algorithm from \textcite{Owoputi2013} was used for both StackOverflow and Twitter to make comparisons across datasets more equitable.

@@

\textcite{Owoputi2013}'s algorithm handles basic word stemming (e.g., removing ``ed'' and ``ing'' endings).
With the StackOverflow dataset however, it is also possible to convert synonym tags to canonical base tags, since the community maintains a tag-synonym database.
This can be thought of as semantic stemming, where two words with identical meaning are converted to the same canonical word.
So tags used for the post were converted to their root tag when possible.

@@

The base-level ($B_{i}$) component in Table \ref{tabACTRBLLModel} is different than the $B_{i}$ used in \textcite{Stanley2013} (Table \ref{tabModACTRModel}).
\citeauthor{Stanley2013} assumed no time dependence, no decay rate, and that the $B_{i}$ is simply a log-odds computation of the probability that each chunk is likely to be presented again, given past frequency.
If a decay rate of 0 is used on the optimized learning form of $B_{i}$, then the equation collapses to $log \left ( n_{i} \right )$,
which is a nonlinear transformation of the $B_{i}$ used by \citeauthor{Stanley2013} ($log \frac{p_{i}}{1-p_{i}}$).
Both forms maintain the same rank ordering, so they should produce similar results.
The $B_{i}$ component used by \citeauthor{Stanley2013} can be roughly thought of as the standard form of $B_{i}$ when the decay rate is 0 (i.e., a pure frequency model).

@@

Given this, it may be worthwhile to use the standard form instead of the optimized learning form when declarative memory is modeled across a broader range of tasks.
However, this should not be taken as a strong recommendation,
since the performance benefits seen in this study could simply be due to the fact that the declarative memory retrievals span across a large period of time, which is not the case for all tasks.
Nonetheless, the only real reason not to use the standard form is due to computational resource limitations.
Since this is becoming less of an issue as hardware speed increases, it may be time to reconsider the default form of base-level learning used in ACT-R.
It may be the case that the optimized learning form of the equation is no longer computationally necessary.
That said, one may still run up against performance limitations when trying to run large-scale models in real-time settings.
Nonetheless, if the standard form is used as the default (or simply tried in another experiment),
the results from this study suggest that the optimal decay rate value should be set slightly higher (\num{0.8}) than the default when optimized learning is used (\num{0.5}).

@@

The ``no processing'' plot shows the size of the spikes when high-frequency words are not removed.
The entropy plot shows how the size decreases by more than an order of magnitude after the entropy weighting measure is used.
The cutoff for the frequency plot was chosen such that the plot looks similar to the entropy plot, with spikes around the same size.
The cutoff that produced the frequency plots in Figures \ref{figContextCutoffSO} and \ref{figContextCutoffT} is where a word represents more than \num{.04}\% of total occurrences in the dataset.

@@

Plots for the three methods of handling stop words for the random permutation model on the StackOverflow dataset are shown in Figure \ref{figContextStopRPSO}.
In the plot, if the model name includes ``full'' then all model components are included.
When the model components are enumerated, then at least one of the components is left out.
For example, the ``standard prior model relaxed across posts'' means that only the prior model component was used when determining activation. 
As another example, ``RP only title with freq'' means that only the title context component of the random permutation model was used, and that stop words were handled using the frequency filtering technique.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsSOPerm-crop.pdf}}}
  \caption{
    Stop-word techniques for the random permutation model for StackOverflow.
    The five methods for handling stop words are shown both for the title model component in isolation and the full model.
    ``Stoplist'', ``freq'', ``entropy'' are the stoplist removal method, removal based on frequency count, and weighting based entropy metric.
    All error bars are the 95\% bootstrapped confidence interval for the mean. 
}
  \label{figContextStopRPSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsTPerm-crop.pdf}}}
  \caption{
  Stop-word techniques for the random permutation model for Twitter.
  The five methods for handling stop words are shown both for the context model component (i.e., no prior term) and the full model.
  All error bars are the 95\% bootstrapped confidence interval for the mean. 
}
  \label{figContextStopRPT}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsSOSji-crop.pdf}}}
  \caption{
  Stop-word techniques for the Bayesian model for StackOverflow
  All error bars are the 95\% bootstrapped confidence interval for the mean. 
}
  \label{figContextStopBSO}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-allWeightingsTSji-crop.pdf}}}
  \caption{
  Stop-word techniques for the Bayesian model for Twitter
  All error bars are the 95\% bootstrapped confidence interval for the mean. 
}
  \label{figContextStopBT}
\end{figure}

@@

The number of documents used to build the co-occurrence matrix has been shown to influence model accuracy \parencite{Sahlgren2008}.
The default number of documents used to build the co-occurrence matrix was \num{1000000} for StackOverflow and \num{3000000} for Twitter.
In order to see how accuracy changed as function of corpus size, 
co-occurrence matrices for a range of smaller corpus sizes were built.

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsSO-crop.pdf}}}
  \caption{
    Random permutation model accuracy when using log-odds transformation on context for StackOverflow
    All error bars are the 95\% bootstrapped confidence interval for the mean. 
  }
  \label{figContextLogoddsSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-logoddsT-crop.pdf}}}
  \caption{
  Random permutation model accuracy when using log-odds transformation on context for Twitter
  All error bars are the 95\% bootstrapped confidence interval for the mean. 
}
  \label{figContextLogoddsT}
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-orderT-crop.pdf}}}
  \caption{
    Model accuracy for various word order methods for the random permutation model for Twitter
    All error bars are the 95\% bootstrapped confidence interval for the mean. 
  }
  \label{figContextOrder}
\end{figure}

@@

The general discussion is separated into two parts.
The first section will describe the overall results,
and the final section will go through each key finding and discuss theoretical implications and future directions for research.

@@

These results provide support for the idea that choosing a hashtag when composing a tweet and tagging a StackOverflow post is akin to a declarative memory retrieval process.
However, both models are not 100 percent accurate, and the amount of variance left to predict is larger than what would be observed if retrieval noise is included in the model.
One possibility that seems likely is that the tag selection process includes other processes besides just declarative memory retrieval
(e.g., strategic processes, determining the number of tags to employ, attempts to add humor).

@@

Even with the large datasets used in this research, there was not enough data on each individual user to build up separate co-occurrence matrices for them.
That is, the context component of the declarative memory models used in this resaerch was formed as a collection of observed co-occurrences across all individuals.
Nonetheless, the prior component for the models was customized for each individual (except in the Twitter popular hashtags dataset when it was not possible).
Ideally, both components would be customized to the individual, and it remains an open question how much accuracy is influenced by using an aggregate or custom context component in the models.

@@

One alternative explanation is that the entropy weighting measure was needed for this research because the contextual co-occurrence matrix was not yet stable, even with these large dataset sizes.
If the matrix was not yet stable, then by chance certain stop words would contribute more net activation to specific tags and introduce noise into the retrieval process for that tag.
So further weighting the contribution of these stop words by leveraging the attentional weight term ensured that this noise was suppressed in the system.
If this is the case, it would be intersting to see how large a dataset is required to not need to modify the attentional weight term.
However even if this is the case, the random permutation model would not be fixed by larger dataset sizes,
since this model simply adds environment vectors to produce the current context vector and has no mechanism (unlike Bayesian normalization) for weighting the contribution of an environment vector.

@@

Nonetheless, it seems likely that the entropy method for computing the attentional weight term $W_{j}$ may be applicable to other declarative memory tasks.
The entropy method is parameter-free (unlike the frequency-filtering method), completely data driven (much like the co-occurrence matrix), does not require tuning,
and substantially increases model accuracy for these datasets.
It is common to handle stop words in some manner when working with Natural Language Processing (NLP) and large text corpuses.
So, if these large corpuses are used to test declarative memory,
then the entropy method may be a more cognitively plausible way of dealing with stop words rather than filtering based on a predetermined list or the frequency count in the dataset.

@@

\subsubsection{Directly Comparing the Models}

After including the prior and entropy components for both models, overall accuracy was similar for the Bayesian and random permutation models for this task.
So it is unclear with this research precisely which model is more cognitively plausible (or if both are correct and simply working at different levels of abstraction).
However, there were two areas in particular where model performance showed relatively large differences: accuracy change as a function of corpus size and reliance on entropy weighting.
These areas could be used in future research to more directly challenge the models.
For example, a domain could be picked where enough data is collected to build a custom co-occurrence matrix for each user.
Then one could look at model accuracy over time for each user as the co-occurrence matrix is increased to see if the trajectory is more accurately modeled by a random permutation (more accurate with lower N) or Bayesian (more accurate with higher N) model.
Further, if a large-scale domain is picked and it is shown that the Bayesian model does not require entropy weighting for the co-occurrence matrix after the representations are fully stabilized,
then this would provide a case where the two models are dramatically different: The random permutation model would require explicitly weighting the stop words (entropy weighting) while the Bayesian model would not.
